%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in} % left page margin
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.2in} % right margin
\addtolength{\topmargin}{-.75in} % moves content up
\addtolength{\textheight}{1.3in} % bottom margin

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large  
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\CertificationSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% \newcommand{\projectSubheading}[2]{
%   \vspace{-0pt}\item
%   \textbf{#1} {\small | #2}
%   \vspace{-8pt}
% }

\newcommand{\projectSubheading}[3]{
  \vspace{-0pt}\item
  \textbf{#1} {\small #2} \hfill {\small #3}
  \vspace{-8pt}
}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{mail@website.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
\begin{center}
    \textbf{\Huge Manish Kumar Sharma} \\
    \vspace{5pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 7897739391 ~ \href{mailto:manish30d@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ manish30d@gmail.com} ~ 
    \href{https://www.linkedin.com/in/mks30d/}{\raisebox{-0.2\height}\faLinkedin\ linkedin.com/in/mks30d}  ~
    \href{https://github.com/Mks30d/}{\raisebox{-0.2\height}\faGithub\ github.com/Mks30d}
    \vspace{0pt}
\end{center}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Flutter Developer}{Jan 2026 - Present}
      {DBS Security Systems Pvt. Ltd.}{Faridabad, India}
      \resumeItemListStart
        \resumeItem{}
          {Implemented biometric unlock flows (Fingerprint, Face) and time-based access restrictions for eKeys, NFC Cards, Fingerprint, Face, and Passcodes, enabling users with more control over the lock.}
        \resumeItem{}
          {Accelerated release cycles by integrating Shorebird for over-the-air (OTA) updates, reducing dependency on manual Play Store deployments.}
        \resumeItem{}
          {Improved production stability of the Endroid ECam app by resolving critical state management and authentication bugs; contributed to Clean Architecture migration, enhancing code scalability and maintainability.}
        \resumeItem{}
          {Mentored a junior intern on Firebase integration and Git workflows, reducing onboarding time and improving team productivity.}
        \resumeItem{\textbf{Exposure:} Flutter, Firebase (Auth, Firestore, Remote Config), TTLock SDK, Shorebird, Provider, Clean Architecture}        
          
      \resumeItemListEnd

    \resumeSubheading
      {Flutter Developer Intern}{Sept - Dec 2025}
      {DBS Security Systems Pvt. Ltd.}{Faridabad, India}
      \resumeItemListStart
        \resumeItem{}
          {Developed advanced lock management features using TTLock SDK, including multi-lock handling, NFC card integration, passcode generation, and eKey sharing with time-based permission controls.}
        \resumeItem{}
          {Architected scalable Firebase integration (Auth + Firestore) powering user account management, lock lifecycle operations (add, update, delete), and multi-lock switching}
        \resumeItem{}
          {Architected a clean, responsive UI/UX with robust state management using Provider, local data persistence via SharedPreferences, and thorough runtime permission handling.}
        \resumeItem{\textbf{Exposure:} Flutter, Firebase (Auth, Firestore), TTLock SDK, Provider, SharedPreferences, Permission Handling}        
          
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages \& Frameworks:- }{Java, Dart, Flutter} \\
     \textbf{Databases:- }{Firebase (Auth, Firestore, Crashlytics, Remote Config)} \\
     \textbf{Tools:- }{Git, GitHub, Postman, Shorebird} \\
     \textbf{Core Skills:- }{App development, Provider, Shared Preferences, SDK Integration, OOPs, Problem-Solving} \\
   }
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\projectSubheading
    {LokTok -}
    {Flutter, Firebase, Provider}
    {\href{https://play.google.com/store/apps/details?id=com.endroid.loktok}{\textcolor{blue}{Play Store}}
    }

\resumeItemListStart
  \resumeItem{}
    {Developed and published a IoT based production Flutter app on Google Play for managing TTLock-based smart handle door locks, featuring nearby lock detection, multi-lock management, and real-time remote/bluetooth based unlocking.}
  \resumeItem{}
    {Implemented multi-mode unlocking feature (Face Recognition, Fingerprint, NFC Card, Passcode) with time-based access control for all credential types, delivering a robust and flexible security layer.}
  \resumeItem{}
    {Deployed OTA updates via Shorebird and ensured production reliability through robust Bluetooth and runtime permission handling, backed by a clean, user-centric responsive UI.}
\resumeItemListEnd

\vspace{-5pt}

\projectSubheading
  {UNIVRSA -}
  {Flutter, Firebase, Provider}
  {\href{https://your-app-link.com} {\textcolor{blue}{App Link}}, 
   \href{https://github.com/Mks30d/Student-App}{\textcolor{blue}{GitHub}}
  }
   
\resumeItemListStart
  \resumeItem{}
    {Developed UNIVRSA, a student management system app using Flutter and Firebase, allowing students to log in and track attendance, assignments, and academic information in real-time.}
  \resumeItem{}
    {Integrated Firebase for authentication, role-based access, and efficient real-time database management.}
  \resumeItem{}
    {Collaborated with a team of three to implement features like notes, PYQs, resource sharing, and user management with seamless real-time updates.}
  % \resumeItem{}
  %   {\textbf{Exposure:} Flutter, Firebase, Shared Preferences}
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Computer Applications}{2023 - 2025}
      {JSS Academy of Technical Education - AKTU}
      {Noida}

      % {Master of Computer Applications}{2023 - 2025}
      % {JSS Academy of Technical Education, Noida - AKTU}{}
    \resumeSubheading
      {Bachelor of Computer Applications}{2019 - 2022}
      {Gandhi Faiz-e-aam College - MJPRU}{Shahjahanpur}

  \resumeSubHeadingListEnd

%-----------Certification-----------------
\section{Certification}
  \resumeSubHeadingListStart

    \CertificationSubheading
      {Full-Stack Web Developer Intern}{Feb - April 2023}
      % {Innomatics Research Labs}{Remote}
      % \resumeItemListStart
        % \resumeItem{}
        %   {Gained exposure in HTML, CSS, JavaScript, Bootstrap, React, Node.js and MongoDB by building multiple project like Notes-Taking App, Covid-19 Tracker, Weather App, and WazirX Clone.}
        % \resumeItem{}
        %   {Developed responsive web applications (Notes App, Covid-19 Tracker, Weather App, WazirX Clone) using HTML, CSS, JavaScript, React, Node.js, and MongoDB with API integration.}
        % \resumeItem{}
        %   {Gained experience in web development by building dynamic, responsive web applications such as a Notes-Taking App, Covid-19 Tracker, Weather App, and WazirX Clone, with a focus on responsive design and API integrations.}
        % \resumeItem{\textbf{Exposure:} HTML, CSS, JavaScript, Bootstrap, React, Node.js and MongoDB}

      % \resumeItemListEnd

    \CertificationSubheading
      {Core Java Developer Intern}{July - Aug 2022}
      % {Precursor Info Solutions Pvt. Ltd.}{Lucknow, India}
      % \resumeItemListStart
        % \resumeItem{}
        %   {Built a Doctor Appointment Management System using Java (J2SE) and MySQL, enabling efficient patient and doctor record management.}
        % \resumeItem{}
        %   {Developed a Doctor Appointment Tracking System using JavaSE and MySQL, enabling nursing home managers and receptionists to efficiently add, update, and manage doctor and patient records.}
        % \resumeItem{\textbf{Exposure:} Java/J2SE, SQL/MySQL}

      % \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Achievements-----------------
\section{Achievements}
    \resumeItemListStart
      \resumeItem{}
        {Secured 4th rank in the CodeQuest coding competition hosted by the Codezen Coding Society, MCA Department.}
    \resumeItemListEnd


%-------------------------------------------
\end{document}
